Psychophysics of musical elements in the discrete-time representation of sound

### 2017-07-01 article/acm/body.tex
melhoradas figuras do artigo

 \begin{figure*}
     \centering
         \includegraphics[width=.7\textwidth]{figures/amostras2c__}
     \caption{Oscillation of 2 samples (maximum frequency for any $f_a$). The first coefficient reflects a detachment (\emph{offset} or \emph{bias}) and the second coefficient specifies the oscillation amplitude.}
         \label{fig:amostras2}
 \end{figure*}

@@

 \begin{figure*}
     \centering
         \includegraphics[width=.7\textwidth]{figures/amostras3b}
     \caption{Three fixed samples present only one non-null frequency. $c_1=c_2^*$ and $w_1 \equiv w_2$.}
         \label{fig:amostras3}
 \end{figure*}

@@

\begin{figure*}
    \centering
        \includegraphics[width=.7\textwidth]{figures/amostras4___}
    \caption{Frequency components for 4 samples.}
        \label{fig:amostras4}
\end{figure*}

@@

\begin{figure*}
    \centering
        \includegraphics[width=.9\textwidth]{figures/amostras4formas__}
    \caption{Basic wave forms with 4 samples.}
        \label{fig:formas4}
\end{figure*}

@@

\begin{figure*}
    \centering
        \includegraphics[width=.7\textwidth]{figures/amostras6_}
    \caption{Frequency components for 6 samples: 4 sinusoids, one of them is the \emph{bias} with zero frequency.}
        \label{fig:amostras6}
\end{figure*}

@@

\begin{figure*}
    \centering
        \includegraphics[width=.9\textwidth]{figures/amostras6formas__}
    \caption{Basic waveforms with 6 samples: triangular and square waveforms have odd harmonics, with different proportions and phases; the sawtooth has even harmonics.}
        \label{fig:formas6}
\end{figure*}

@@

\begin{figure}[h!]
    {\centering
        \includegraphics[width=.7\columnwidth]{figures/mixagem_}}
    \caption{Mixing of three sound sequences. The amplitudes are directly overlapped.}
        \label{fig:mixagem}
\end{figure}

@@

\begin{figure}[h!]
{    \centering
        \includegraphics[width=.5\columnwidth]{figures/concatenacao_}}
    \caption{Concatenation of three sound sequences by temporal overlap of their samples.}
        \label{fig:concatenacao}
\end{figure}

@@

\begin{figure*}
    \centering
        \includegraphics[width=\textwidth]{figures/lut}
    \caption{Search in the \emph{lookup table} to synthesize sounds at different frequencies using a unique waveform with high resolution.}
        \label{fig:lut}                                                                                                            
\end{figure*}

@@

\begin{figure}[h!]
     \centering
         \includegraphics[width=\columnwidth]{figures/transicao}
     \caption{Intensity transitions for different values of $\alpha$ (see equations~\ref{seqAmp} and ~\ref{transAmp}).}
         \label{fig:transicao}
\end{figure}

@@

\begin{figure*}
    \centering
        \includegraphics[width=\textwidth]{figures/delays}
    \caption{Convolution with the impulse: shifting (a), delay lines (b) and granular synthesis~(c). Represented in increasing order of its pulse density.}
        \label{fig:delays}
\end{figure*}

>>>>

 \begin{figure*}
     \centering
         \includegraphics[width=.7\textwidth]{figures/amostras2c___}
     \caption{Oscillation of 2 samples (maximum frequency for any $f_a$). The first coefficient reflects a detachment (\emph{offset} or \emph{bias}) and the second coefficient specifies the oscillation amplitude.}
         \label{fig:amostras2}
 \end{figure*}

@@

 \begin{figure*}
     \centering
         \includegraphics[width=.7\textwidth]{figures/amostras3b_}
     \caption{Three fixed samples present only one non-null frequency. $c_1=c_2^*$ and $w_1 \equiv w_2$.}
         \label{fig:amostras3}
 \end{figure*}

@@

\begin{figure*}
    \centering
        \includegraphics[width=.7\textwidth]{figures/amostras4____}
    \caption{Frequency components for 4 samples.}
        \label{fig:amostras4}
\end{figure*}

@@

\begin{figure*}
    \centering
        \includegraphics[width=.9\textwidth]{figures/amostras4formas___}
    \caption{Basic wave forms with 4 samples.}
        \label{fig:formas4}
\end{figure*}

@@

\begin{figure*}
    \centering
        \includegraphics[width=.7\textwidth]{figures/amostras6__}
    \caption{Frequency components for 6 samples: 4 sinusoids, one of them is the \emph{bias} with zero frequency.}
        \label{fig:amostras6}
\end{figure*}

@@

\begin{figure*}
    \centering
        \includegraphics[width=.9\textwidth]{figures/amostras6formas___}
    \caption{Basic waveforms with 6 samples: triangular and square waveforms have odd harmonics, with different proportions and phases; the sawtooth has even harmonics.}
        \label{fig:formas6}
\end{figure*}

@@

\begin{figure}[h!]
    {\centering
        \includegraphics[width=.5\columnwidth]{figures/mixagem__}}
    \caption{Mixing of three sound sequences. The amplitudes are directly overlapped.}
        \label{fig:mixagem}
\end{figure}

@@

\begin{figure}[h!]
{    \centering
        \includegraphics[width=.5\columnwidth]{figures/concatenacao__}}
    \caption{Concatenation of three sound sequences by temporal overlap of their samples.}
        \label{fig:concatenacao}
\end{figure}

@@

\begin{figure*}
    \centering
        \includegraphics[width=.7\textwidth]{figures/lut_}
    \caption{Consultation in the \emph{lookup table} to synthesize sounds at different frequencies using a unique waveform with high resolution.
	Each \emph{i-th} sample $t_i^f$ of a sound with frequency $f$ is related to the samples in the table $\widetilde{l}$\, by the relation $t_i^{f}=\widetilde{l}_{\left\lfloor i.f\frac{\widetilde{\Lambda}}{f_a} \right\rfloor \%\,\widetilde{\Lambda}}$ where $\widetilde{\Lambda}$ is the number of sample in $\widetilde{l}$ and $f_a$ is the sampling rate.}
        \label{fig:lut}                                                                                                            
\end{figure*}

@@

\begin{figure}[h!]
     \centering
         \includegraphics[width=.7\columnwidth]{figures/transicao_}
     \caption{Intensity transitions for different values of $\alpha$ (see equations~\ref{seqAmp} and ~\ref{transAmp}).}
         \label{fig:transicao}
\end{figure}

@@

\begin{figure*}
    \centering
        \includegraphics[width=\textwidth]{figures/delays_}
    \caption{Convolution with the impulse: shifting (a), delay lines (b) and granular synthesis~(c). Represented in increasing order of its pulse density.}
        \label{fig:delays}
\end{figure*}
